### 2014-11-10 CVPR/Source/localize.tex
Reorganized paper tex files

\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
%%%%%%%%%%% CVPR template packages end %%%%%%%%%%%%%%
\usepackage{verbatim} % for comment environment
% \usepackage{soul} % for \hl highlighting
% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

%\cvprfinalcopy % *** Uncomment this line for the final submission

\def\cvprPaperID{489} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

% 3D pose of the cars and ego motion
\newcommand{\pos}[2]{\mathbf{p}^{(#1)}(#2)}
\newcommand{\ori}[2]{\mathbf{\omega}^{(#1)}(#2)}
\newcommand{\state}[2]{\mathbf{s}^{#1}(#2)}

% ego pose
\newcommand{\egop}[1][t]{\pos{c}{#1}}
\newcommand{\egoo}[1][t]{\ori{c}{#1}}
\newcommand{\egos}[1][t]{\state{c}{#1}}

% relative pose between camera and car $i$
\newcommand{\relp}[2]{\Omega^{#1}(#2)}
\newcommand{\relpz}[2]{\Omega_z^{#1}(#2)}

% 3D tracks on car $i$ in its own coordinate frame
\newcommand{\tracklets}{\mathbf{X}^{(i)}_o}
\newcommand{\tracklet}[1]{\mathbf{x}^{(i)}_{#1}}
% track projections on camera
\newcommand{\trackp}[1]{\mathbf{u}^{(i)}(#1)}
\newcommand{\trackpj}[1]{\mathbf{u}_j(#1)}
% Unclassified track point projected on camera
\newcommand{\ucTrackp}{\mathbf{u}(t)}

% dimensions of car $i$
\newcommand{\dimsn}[1]{\mathbf{B}^{#1}}
\newcommand{\expDimsn}{\hat{\mathbf{B}}}

% projection function
\newcommand{\projectionOf}[1]{\pi_{\relp{i}{t}}\left(#1\right)}
\newcommand{\projectionOft}[1]{\pi_{\relp{i}{t+1}}\left(#1\right)}
\newcommand{\centerProj}{\bar{\pi}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\cornerProj}[1]{\pi^{#1}_{\relp{i}{t}}(\dimsn{i})}
\newcommand{\triangleProj}[1]{\triangle^{#1}_{\relp{i}{t}}(\dimsn{i})}

% bounding box corners on image
\newcommand{\bb}[1]{\mathbf{d}^{#1}(t)}

\newcommand{\Energy}[1]{\mathcal{E}^{it}_{\text{#1}}}
\newcommand{\pEnergy}[1]{\mathcal{E}^{ijt}_{\text{#1}}}
% Weighted energy
\newcommand{\WEnergy}[1]{\lambda_{\text{#1}}\Energy{#1}}
\newcommand{\EnergyCol}{\mathcal{E}^{ijt}_{\text{col}}}
\newcommand{\WEnergyCol}{\lambda_{\text{col}}\EnergyCol}

\newcommand{\occFreeProj}[1]{\Pi_{\relp{i}{t}}(#1)}
\newcommand{\minx}{x_{\text{min}}}
\newcommand{\miny}{y_{\text{min}}}
\newcommand{\maxx}{x_{\text{max}}}
\newcommand{\maxy}{y_{\text{max}}}
\newcommand{\frontface}{F^i_\text{FF}(t)}

\newcommand{\occ}[1]{o({#1})}
\newcommand{\face}{F^i_k(t)}

\newcommand{\invProjectionOf}[1]{\pi^{-1}_{\relp{i}{t}}\left(#1\right)}
\newcommand{\occf}{f^i_{occ}(\mathbf{x}_j)}
\newcommand{\occftot}{f_{occ}(\mathbf{x}_j)}
\newcommand{\occft}[1]{f_{occ}(#1)}

\newcommand{\ray}{\hat{\mathbf{r}}_j}
\newcommand{\occfray}{f_{occ}(\lambda\ray)}
\newcommand{\lambdadist}{f_{\lambda}(\trackpj{t-1}, \lambda)}

\newcommand{\occfxi}{L(\mathbf{x}; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\occfi}{L(\lambda \ray; \pos{i}{t-1}, \Sigma_i)}
\newcommand{\assocP}{a^{(ij)}(\lambda)}
\newcommand{\assocPk}{a^{(ij)}(\lambda_k)}

\newcommand{\Ereproj}{E^{(ij)}_{\text{reproj}}}
\newcommand{\Ptrans}{P^{(j)}_{\text{transmission}}(\lambda)}
\newcommand{\Ptransmud}{P^{(j)}_{\text{transmission}}(\mu^{(i)}_d)}
\newcommand{\Prefl}{P^{(ij)}_{\text{reflection}}(\lambda)}
\newcommand{\dishort}{d_i(\mathbf{x})}

\newcommand{\Lu}{L_u(\mathbf{u}, \mu^i_u,\Sigma^i_u)}
\newcommand{\Llambda}{L_{\lambda}(\mathbf{u}, \lambda; \mu^i_d)}

\newcommand{\Gauss}{\mathcal{N}}
\newcommand{\PropDist}{\mathcal{W}_j}

\newcommand{\muijl}{\mu^{(ij)}_{\lambda}}
\newcommand{\sigmaijl}{\sigma^{ij}_{\lambda}}

\newcommand{\Sigmait}{\Sigma^{(i)^{-1}}_t}

\newcommand{\muit}{\mu^(i)_t}
\newcommand{\Sigmaic}{\Sigma'^{(i)^{-1}}_c}

\newcommand{\muic}{{\mu^(i)_c}}
\newcommand{\Sigmaicf}{\Sigma^{(i)^{-1}}_c}

\newcommand{\muiu}{\mu^{(i)}_t}
\newcommand{\Sigmaiu}{\Sigma^{(i)^{-1}}_u}

\newcommand{\xt}{\mathbf{x}_t}
\newcommand{\xc}{\mathbf{x}_c}

\newcommand{\Rctot}{R}
\newcommand{\tctot}{t}

\newcommand{\tcmut}{t'}

\newcommand{\Beizer}{B\'eizer }

\newcommand{\LaneUncertainty}[1]{\Sigma_{L_m}(#1)}
\newcommand{\projOnLane}[1]{\pi_{L_m(k)}(#1)}

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
%\setcounter{page}{4321}
%\DeclareMathSymbol{\Tangent}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\poly}{poly}
\DeclareMathOperator*{\argmin}{\arg\min}

\begin{document}
\title{Continuous Models for Scene and Traffic Participant Interactions in Road Scene Understanding.}
\author{Vikas Dhiman\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small dhiman@umich.edu}
\and
Manmohan Chandraker\\
NEC Laboratories America, Inc.\\
Cupertino, CA, USA\\
{\tt\small manu@nec-labs.com}
\and
Jason J Corso\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small jjcorso@eecs.umich.edu}
}
\maketitle

%%%%%%%%% ABSTRACT
\begin{abstract}
  TODO: Write abstract
  \vspace{4cm}
\end{abstract}

\section{Introduction}

\begin{itemize}
  \item Introduce the problem
  \item Describe our approach
  \item Contrast with Milan's work
  \item Contrast with Andreas Geiger's work
  \item Highlight the contributions
\end{itemize}
\vspace{10cm}
\begin{figure}[t]
  \includegraphics[width=\columnwidth]{graphics/graphicalModelFrom61ConstVars.pdf}
  \caption{Graphical model. The six numbered black circles represent the
    unknown state variables of each car. All other nodes in the graphical model
    are assumed
    observed variables. Consider each energy in the model one by one. (1)
    Bounding box energy: The bounding box energy without occlusion modeling is
    a unary term, but with occlusion it becomes a higher order term that
    affects the state of occluder as well. In this graphical model we assume
    that the scene is being observed from left to right, hence "2" occludes "6"
    and "5" and "5" occludes "1". The bounding box detection is represented by
  $\mathbf{d}_{bb}^i(t)$ and the statistical dependencies are represented by
  red lines. (2) Point tracks ($\Energy{track}$): Since occlusion is also
  included in modeling point tracks energy we have similar interdependencies
  for point tracks energy. The available point tracks are modeled by
  $\mathbf{u}(t)$. (3) Collision ($\Energy{coll}$) : The collision energy
  mathematically is a dense graph between all the TP but here we represent
  collision among only those TP that are near enough to have a significant
collision energy. (4) Orientation from detection ($\Energy{ori}$) (5) Orientation from lane (and map) information ($\Energy{lane}$)}
  \label{fig:graphmodel}
\end{figure}

\section{Related Work}
TODO:
\vfill
\pagebreak
Related work continued
\vspace{15cm}

\section{Problem Definition}
TODO:
\vspace{4cm}

\section{Notation}

\begin{table}[h]
  \begin{tabular}{|l|l|}
    \hline
    Symbol & Meaning \\
    \hline
    $\pos{i}{t}$ & Position of $i$th car at time $t$\\
    $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
     $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
    $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
    $\egop$ & Position of camera at time $t$\\
    $\egoo$ & Orientation of camera at time $t$\\
    $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
    $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
    $\trackp{t}$ & Projection of $\tracklets$ in camera\\
    $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
    $\bb{i}$ & 2D bounding box of the car in image\\
    \hline
  \end{tabular}
\end{table}

%%%%%%%%% BODY TEXT
\section{The Model}

The objective is to find the most likely traffic participant (TP) state given
various evidences $\mathbb{E} = \{\{\trackp{t}\}, \{\bb{i}\}, \text{lane det.},
\text{map}, \text{GPS}\}$.

Mathematically, find:
\begin{align}
  \{\state{i}{t}\}^* &= \arg \max P(\{\state{i}{t}\} | \mathbb{E})
\end{align}

Bayes rule
\begin{align}
  P(\{\state{i}{t}\} | \mathbb{E}) &=
  \frac{1}{Z}P( \mathbb{E} | \{\state{i}{t}\})P(\{\state{i}{t}\})
\end{align}

Assume conditional independence according to graphical model in
\ref{fig:graphmodel}.

\begin{multline}
  P(\{\state{i}{t}\} | \mathbb{E}) =
  \frac{1}{Z}
  \prod_{t=s_i}^{e_i}\prod_{i,j: i \ne j}(P(\state{i}{t}, \state{j}{t}))\\
%
  \prod_{i=1}^{N}
  \prod_{t=s_i}^{e_i}
  P(\bb{i} | \state{i}{t})
  P(\trackp{t} | \state{i}{t})\\
  P(\state{i}{t} | L_m(t))
  P(\state{i}{t} | \state{i}{t-1})
  P(\state{i}{t})
\end{multline}

We can formulate similar objective function in negative log domain:
\footnote{TODO:Resolve inconsistency in summation absorption in energy terms.}
\begin{multline}
  -\log{P(\{\state{i}{t}\} | \mathbb{E})} = 
  Z' + \sum_{i,j:i\ne j} \sum_{t=s_i}^{e_i}  \WEnergyCol \\
  + \sum_{i=1}^N \sum_{t=s_i}^{e_i}
    \WEnergy{box}
  + \WEnergy{track}\\
  + \WEnergy{lane}
  + \WEnergy{dyn}
  + \WEnergy{prior}
\end{multline}

\section{Modeling traffic participants}
\label{sec:TPmodel}
Following standard model of occupancy in 3D reconstruction community, we model
the TP's as high occupancy regions in space. We model the
uncertainty in occupancy equivalent of transparency i.e. the regions that are
more certain to be occupied are viewed as relatively more opaque then other
regions. Based on this intuition we model TP's translucent
ellipsoids whose opacity is maximum at the center and drops off away from the
center. More specifically we model, the occupancy of a TP as a
logistic function,

\begin{align}
   \occf = L(\mathbf{x}; \pos{i}{t}, \Sigma_i)
\end{align}
where $L(.)$ is the logistic function defined by
\begin{align}
  L(\mathbf{x}; \pos{i}{t}, \Sigma_i) = \frac{1}{
    1 + e^{-k(1 - d(\mathbf{x},\pos{i}{t}))}
    }
\end{align}
where $d(\mathbf{x},\pos{i}{t}) =
(\mathbf{x}-\pos{i}{t})^\top\Sigma_i(\mathbf{x}-\pos{i}{t})$ and $k =
10\ln{49}$. $k$ is chosen such that $L(.) = 0.98$ when $d(.) =
0.9$. $\Sigma_i$ determines the spread of the ellipsoid and depends on the
dimensions of the TP. Please refer to supplementary material 
for computation of $\Sigma_i$ from TP's dimensions.

We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
(1) reflection and (2) transmission through intermediate space. The reflection
part ensures that there is an object to reflect a point at a certain region in
the 3D space while transmission part models occlusion.
\begin{align}
  P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
\end{align}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Reflection probability}
For Lambertian reflection we replace the surface normal with the
gradient of occupancy.
%
\begin{align}
  \Prefl = (\max \{0, \nabla \occf^\top
  \hat{\mathbf{r}_j}\})^2
\end{align}
%
where $\ray =
\frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
direction of ray. The gradient in the direction opposite to ray yields -ve
probability which needs to be clipped off. Squaring the function keep it
smooth near zero.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Transmission probability}
A model for transmission of light through a material of thickness $x$,
density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
%
\begin{align}
  I(x) = I_0e^{-k_o\rho x}
\end{align}
%

Since both opacity and density are represented by the occupancy function
$\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
\infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
function $1 - \occftot$. So the transmission probability over a small distance
$d\lambda$ is given by
%
\begin{align}
  P_{\text{transmission}}(\lambda + d\lambda) =
  P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
\end{align}
%

For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by

\begin{align}
  %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
  \Ptrans &=
  \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
  %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
  %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
  \label{eq:ptrans-integral}
\end{align}
where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
$\lambda$.

In practice, the integral for transmission probability
\eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
choose a product of sigmoid function that approximates the behaviour of
transmission probability,
%
\begin{align}
\label{eq:evalCumulativePtrans}
  \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
\end{align}
%
where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
representing the elliptical projection of $i^{th}$ TP.
$L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
depth of the $i^{th}$ TP.
%
\begin{align}
  L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
    1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
    \muiu))}
  }
  \\
  L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
    1 + e^{-k_d(\lambda - \mu^i_d)}
}
\end{align}
%

\begin{comment}%% Comment
  A product integral is a simple integral in log domain
  \begin{align}
    \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
    e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
  \end{align}
\end{comment}%% Comment

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Energies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We explain energies in this section

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Association error evaluation}

To verify the correctness of our association probability $\assocP$ we perform
association error experiment that compare the accuracy of point track
association with TPs with that of bounding box baseline method.

% \begin{align}
%   f^{i}_{reproj}&(\trackpj{t-1}, \lambda) =
%   \projectionOf{\invProjectionOf{\trackpj{t-1}}}\\
%   %&= K(R^i_t ((R^i_{t-1})^\top\lambda \ray - (R^i_{t-1})^\top T_{t-1}) + T_{t})\\
%   &= \frac
%   {p_{1:2}\lambda + q_{1:2}}
%   {p_{3}\lambda + q_{3}}
% \end{align}
% where $p_{1:3} = KR^i_t(R^i_{t-1})^\top\ray$ and
% $q_{1:3} = KR^i_t(R^i_{t-1})^\top T_{t-1} + KT_t$
% 
% Now that we have an association from TP $i$ to point track $j$ through
% $\lambda$, we can come up with an association probability
% \begin{align}
%    \assocP &= \frac{(\max \{ 0, \nabla \occf^\top
% \ray \})^2 }{P_{\text{reflection}}}\lambdadist\\
% &=(\max \{ 0, \nabla \occf^\top \ray \})^2
%   \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
% \end{align}

Note that the fraction $\assocP$ although called association probability does
not capture the entire information that we have available for compute
association of points to tracks. This above fraction is the association
probability given the hypothesized parameters of TP model.

To compute the association probability between TP $i$ and
point track $j$ we must use re-projection error as well. When the association
$i$ and $j$ is right and the point of reflection is at depth $\lambda$ the
re-projection error must be zero \eqref{eq:reprojerror}, otherwise the error
becomes a measure of distance from the true solution.
The error terms can be converted to probability domain by considering the error
term as negative log of probability

\begin{align}
  P^{(ij)}_{\text{assoc by reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda))
\end{align}

Using both the evidence terms we can write probability of association as
\begin{align}
  P^{(ij)}_{\text{assoc}} = \frac{1}{Z'}\int_0^{\infty} \assocP \frac{1}{\sqrt{2\pi}}\exp(-\Ereproj(\lambda))d\lambda
  \label{eq:prob-assoc}
\end{align}

Once we have the probability of association we can compute the best possible
assignment of TP for each point. The points having very small association
probability are assigned to the background,
\begin{align}
  i^*_{j} = \argmin_{i} \int_0^\infty \assocP \Ereproj(\lambda) d\lambda
\end{align}

We use bounding box based assignment of point tracks to TPs as the baseline.
For the regions where the bounding boxes overlap, we assign the points to the
TP that has smaller mean depth then the competing bounding box.

{\small
\bibliographystyle{ieee}
\bibliography{model}
}
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Continuous Energies for Object Localization}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We explain energies in this section.

@@
